maze-dataset: Maze Generation with Algorithmic Variety and Representational Flexibility

### 2025-08-04 docs/paper/paper.tex
figure 6 fixed?
fix figure 4
table 1 working
fix figure 7
fix citations, full paper compiling but fig heights messed up
figure sizing, formatting edits

Solving mazes is a classic problem in computer science and artificial
intelligence, and humans have been constructing mazes for thousands of
years. Although finding the shortest path through a maze is a solved
problem, this very fact makes it an excellent testbed for studying how
machine learning algorithms solve problems and represent spatial
information. We introduce \texttt{maze-dataset}, a user-friendly Python
library for generating, processing, and visualizing datasets of mazes.
This library supports a variety of maze generation algorithms providing
mazes with or without loops, mazes that are connected or not, and many
other variations. These generation algorithms can be configured with
various parameters, and the resulting mazes can be filtered to satisfy
desired properties. Also provided are tools for converting mazes to and
from various formats suitable for a variety of neural network
architectures, such as rasterized images, tokenized text sequences, and
various visualizations. As well as providing a simple interface for
generating, storing, and loading these datasets, \texttt{maze-dataset}
is extensively tested, type hinted, benchmarked, and documented.

@@

@@

@@

>>>>

Solving mazes is a classic problem in computer science and artificial
intelligence, and humans have been constructing mazes for thousands of
years. Although finding the shortest path through a maze is a solved
problem, this very fact makes it an excellent testbed for studying how
machine learning algorithms solve problems and represent spatial
information. We introduce \texttt{maze-dataset}, a user-friendly Python
library for generating, processing, and visualizing datasets of mazes.
This library supports a variety of maze generation algorithms which can
be configured with various parameters, and the resulting mazes can be
filtered to satisfy desired properties. Also provided are tools for
converting mazes to and from various formats suitable for a variety of
neural network architectures, such as rasterized images, tokenized text
sequences, and various visualizations. As well as providing a simple
interface for generating, storing, and loading these datasets,
\texttt{maze-dataset} is extensively tested, type hinted, benchmarked,
and documented.

@@

\input{figures/tex/fig4_tokenfmt.tex}

@@

\input{figures/tex/tab1_benchmarks.tex}

\input{figures/tex/fig6_benchmarks.tex}

\input{figures/tex/fig7_sre.tex}

@@

\input{figures/tex/fig8_impl.tex}
